Coupling finite and boundary element methods to solve the Poisson--Boltzmann equation for electrostatics in molecular solvation

### 2023-05-05 main.tex
small tweaks

\subsection*{\sffamily \large DATA AVAILABILITY STATEMENT}
All codes to reproduce the results of this manuscript can be found in the GitHub repository \url{https://github.com/MichalBosy/FEM_BEM_coupling/}, alongside links to Docker images
that include the codes alongside installations of appropriate versions of Bempp-cl and FEniCSx.

>>>>

\subsection*{\sffamily \large DATA AVAILABILITY STATEMENT}
All codes to reproduce the results of this manuscript can be found in the GitHub repository \href[https://github.com/MichalBosy/FEM_BEM_coupling/]{github.com/MichalBosy/FEM_BEM_coupling}, alongside links to Docker images
that include the codes alongside installations of appropriate versions of Bempp-cl and FEniCSx.

### 2023-05-05 results.tex
small tweaks

Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available ( \url{https://bempp.com/installation.html}), and all codes used to generate the results in this section are available as Jupyter Notebooks that can be reproducibly executed in an appropriate environment. The results in this section were obtained using version 0.6.0 of FEniCSx and version 0.3.0 of Bempp-cl. All codes to reproduce the results of this manuscript can be found in the GitHub repository \url{https://github.com/MichalBosy/FEM_BEM_coupling/}.

@@

In the experiments presented so far, we have only tested the FEM-BEM coupled approach with small structures. In this section, we study its behaviour with larger structures to evaluate its applicability in more realistic settings, and in test cases where BEM-BEM coupling is not an alternative. Using the same Gaussian permittivity field inside the molecule, we computed the solvation free energy of protein G B1 (955 atoms, PDB code 1pgb), lysozyme (1960 atoms, PDB code 1lyz), the barnase-barstar complex (9464 atoms, PDB code 1x1u), and immunoglobulin G (20148 atoms, PDB code 1igt). All structures were parameterized with the Amber\cite{Swanson05} force field using pdb2pqr.\cite{Dolinsky04} The surfaces were meshed with Nanoshaper\cite{decherchi2013general} using a grid scale of 1.5, and then volume meshes were generated using pyGAMer\cite{lee2020open} and TetGen\cite{hang2015tetgen} with a radius-edge ratio of 1.0. The solvation free energy and timings for these runs are presented in Table \ref{table:large_variable}. These results demonstrate that FEM-BEM coupling implementation can reach medium-to-large-sized proteins on a simple workstation. For these larger structures, we enabled the FMM capabilities of Bempp-cl.

>>>>

Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available (\href[https://bempp.com/installation.html]{bempp.com/installation.html}), and all codes used to generate the results in this section are available as Jupyter Notebooks that can be reproducibly executed in an appropriate environment. The results in this section were obtained using version 0.6.0 of FEniCSx and version 0.3.0 of Bempp-cl. All codes to reproduce the results of this manuscript can be found in the GitHub repository \href[https://github.com/MichalBosy/FEM_BEM_coupling/]{github.com/MichalBosy/FEM_BEM_coupling}.

@@

In the experiments presented so far, we have only tested the FEM-BEM coupled approach with small structures. In this section, we study its behaviour with larger structures to evaluate its applicability in more realistic settings, and in test cases where BEM-BEM coupling is not an alternative. Using the same Gaussian permittivity field inside the molecule, we computed the solvation free energy of protein G B1 (955 atoms, PDB code 1pgb), lysozyme (1960 atoms, PDB code 1lyz), the barnase-barstar complex (9464 atoms, PDB code 1x1u), and immunoglobulin G (20148 atoms, PDB code 1igt). All structures were parameterized with the Amber\cite{Swanson05} force field using pdb2pqr.\cite{Dolinsky04} The surfaces were meshed with Nanoshaper\cite{decherchi2013general} using a grid scale of 1.5, and then volume meshes were generated using pyGAMer\cite{lee2020open} and TetGen\cite{hang2015tetgen} with a radius-edge ratio of 1.0. The solvation free energy and timings for these runs are presented in Table \ref{table:large_variable}. These results demonstrate that our FEM-BEM coupling implementation can reach medium-to-large-sized proteins on a simple workstation. For these larger structures, we enabled the FMM capabilities of Bempp-cl.
